---
title: "Get rid of renderUI"
author: "David Granjon"
date: "8/23/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(bs4Dash)
```

## With renderUI

`renderUI`will make the entire dropdown menu re-render each time something changes in the renderUI expression, which may not be optimal. For instance in React, we only re-render what needs to be updated!

```{r, eval=FALSE}
shinyApp(
  ui = bs4DashPage(
    navbar = bs4DashNavbar(
      rightUi = uiOutput("menu", container = tags$li)
    ),
    sidebar = bs4DashSidebar(),
    controlbar = bs4DashControlbar(),
    footer = bs4DashFooter(),
    title = "test",
    body = bs4DashBody()
  ),
  server = function(input, output, session) {
    output$menu <- renderUI({
      dropdownMenu(
        show = FALSE,
        status = "danger",
        src = "https://www.google.fr",
        dropdownMenuItem(
          message = "message 2",
          from = "Nono Gueye",
          src = "https://adminlte.io/themes/v3/dist/img/user3-128x128.jpg",
          time = "yesterday",
          status = "success",
          type = "message"
        )
      )
    })
  }
)
```

## With JS

### Why don't we just go for `insertUI()`?
Let's try below

```{r, eval=FALSE}
shinyApp(
  ui = bs4DashPage(
    navbar = bs4DashNavbar(
      rightUi = dropdownMenu(
        show = FALSE,
        status = "danger",
        src = "https://www.google.fr"
      )
    ),
    sidebar = bs4DashSidebar(),
    controlbar = bs4DashControlbar(),
    footer = bs4DashFooter(),
    title = "test",
    body = bs4DashBody(actionButton("add", "Add dropdown item"))
  ),
  server = function(input, output, session) {
    
    observeEvent(input$add, {
      insertUI(
        selector = ".dropdown-menu > .dropdown-divider",
        where = "afterEnd",
        ui = dropdownMenuItem(
          inputId = paste0("triggerAction_", input$add),
          message = paste("message", input$add),
          from = "Divad Nojnarg",
          src = "https://adminlte.io/themes/v3/dist/img/user3-128x128.jpg",
          time = "today",
          status = "danger",
          type = "message"
        )
      )
    }, priority = 2)
  }
)
```

Well, if the item is inserted, the item counter as well as the dropdown text are not! We may fix that
by adding extra `insertUI()` and `removeUI()` to replace those parts of the interface (`insertUI()` does not update
the targeted item). Moreover, you we must set correct priority to each observeEvent (try to remove them, it will fail) to ensure that _remove_ happens before _insert_. 

```{r, eval=FALSE}
shinyApp(
  ui = bs4DashPage(
    navbar = bs4DashNavbar(
      rightUi = dropdownMenu(
        show = FALSE,
        status = "danger",
        src = "https://www.google.fr"
      )
    ),
    sidebar = bs4DashSidebar(),
    controlbar = bs4DashControlbar(),
    footer = bs4DashFooter(),
    title = "test",
    body = bs4DashBody(actionButton("add", "Add dropdown item"))
  ),
  server = function(input, output, session) {
    
    observeEvent(input$add, {
      insertUI(
        selector = ".dropdown-menu > .dropdown-item.dropdown-footer",
        where = "beforeBegin",
        ui = dropdownMenuItem(
          inputId = paste0("triggerAction_", input$add),
          message = paste("message", input$add),
          from = "Divad Nojnarg",
          src = "https://adminlte.io/themes/v3/dist/img/user3-128x128.jpg",
          time = "today",
          status = "danger",
          type = "message"
        )
      )
    })
    
    # remove old badge
    observeEvent(input$add, {
      removeUI(selector = ".badge-danger.navbar-badge")
    }, priority = 1)
    
    # insert new badge
    observeEvent(input$add, {
      insertUI(
        selector = "[data-toggle=\"dropdown\"]",
        where = "beforeEnd",
        ui = tags$span(class = "badge badge-danger navbar-badge", input$add)
      )
    })
    
    
    # remove old text counter
    observeEvent(input$add, {
      removeUI(selector = ".dropdown-item.dropdown-header")
    }, priority = 1)
    
    # insert new text counter
    observeEvent(input$add, {
      insertUI(
        selector = ".dropdown-menu",
        where = "afterBegin",
        ui = tags$span(class="dropdown-item dropdown-header", sprintf("%s Items", input$add))
      )
    })
    
  }
)
```

So many `observeEvent` for a simple action! Imagine if we had 10 similar tasks... Isn't there a way to do all of this at once, thereby reducing the server code?

### Pure JS solution

In the following we'll do most of the work in JavaScript. I must acknowledge it' s not as easy as with `renderUI()` nor `insertUI()`.

We create the `insertDropdownItem` function with 2 parameters:

- item 
- session

item is convert to a character (important) and sent to JavaScript through the shiny session R6 object. We give it a type, that is 'add-item', to be able to identify it from JavaScript with `Shiny.addCustomMessageHandler`.

```{r, eval=FALSE}
insertDropdownItem <- function(item, session = shiny::getDefaultReactiveDomain()) {
  session$sendCustomMessage("add-item", message = as.character(item))
}
```

We recover the sent message on the JS side with `Shiny.addCustomMessageHandler`, then parse the string to HTML with `$.parseHTML` and insert it before the footer (that is the next UI element of the dropdown body). We also update dropdown menu item counter as well as the icon text since the dropdown menu is not re-rendered.

```{javascript}
$(function() {
  Shiny.addCustomMessageHandler('add-item', function(message) {
    // convert string to HTML
    var itemTag = $.parseHTML(message)[0];
    $(itemTag).insertBefore($('.dropdown-item.dropdown-footer'));
    // since we do not re-render the dropdown, we must update its item counter
    var $items = $('button.dropdown-item').length;
    $('.dropdown-item.dropdown-header').html($items + ' Items');
    $('.nav-item.dropdown').find('.navbar-badge').html($items);
  });
});
```

The whole code below.

```{r, eval=FALSE}
shinyApp(
  ui = bs4DashPage(
    navbar = bs4DashNavbar(
      rightUi = dropdownMenu(
        show = FALSE,
        status = "danger",
        src = "https://www.google.fr"
      )
    ),
    sidebar = bs4DashSidebar(),
    controlbar = bs4DashControlbar(),
    footer = bs4DashFooter(),
    title = "test",
    body = bs4DashBody(
      tags$head(
        tags$script(
          "$(function() {
            Shiny.addCustomMessageHandler('add-item', function(message) {
              // convert string to HTML
              var itemTag = $.parseHTML(message)[0];
              $(itemTag).insertBefore($('.dropdown-item.dropdown-footer'));
              // since we do not re-render the dropdown, we must update its item counter
              var $items = $('button.dropdown-item').length;
              $('.dropdown-item.dropdown-header').html($items + ' Items');
              $('.nav-item.dropdown').find('.navbar-badge').html($items);
            });
          });
          "
        )
      ),
      actionButton("add", "Add dropdown item")
    )
  ),
  server = function(input, output, session) {
    
    observeEvent(input$add, {
      insertDropdownItem(
        dropdownMenuItem(
          inputId = paste0("triggerAction_", input$add),
          message = paste("message", input$add),
          from = "Divad Nojnarg",
          src = "https://adminlte.io/themes/v3/dist/img/user3-128x128.jpg",
          time = "today",
          status = "danger",
          type = "message"
        )
      )
    })
  }
)
```

As shown above, this solution significantly lightens the server code since everything may be done
on the JS side in 1 step. 

We might improve the previous function by adding the possibility to insert multiple items. 
