---
title: "bulmajs"
author: "David Granjon"
date: "9/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
library(jsonlite)
dropNulls <- function(x) {
  x[!vapply(x, is.null, FUN.VALUE = logical(1))]
}
```

## bulmajs
As stated in the previous activity, bulma only contains CSS things! It means we need
either to develop custom JS code to add interactivity or use any existing API. 
[bulma JS](https://bulmajs.tomerbe.co.uk/) is one of these!

### Add the dependency
```{r bulmajs-deps}
bulma_js_dep <- htmlDependency(
  name = "bulmajs",
  version = "0.11.0",
  src = c(href = "https://cdn.jsdelivr.net/npm/@vizuaalog/bulmajs@0.11.0/dist"),
  script = "bulma.js"
)

use_bulmajs <- function(tag) {
  tagList(tag, bulma_js_dep)
}
```

### Notification 
```{r nulma-notif}
show_bulma_notification <- function(id = NULL, options = NULL, session = shiny::getDefaultReactiveDomain()) {
  message <- dropNulls(
    list(
      id = id,
      options = dropNulls(options)
    )
  )
  session$sendCustomMessage(type = "bulma-notif", message)
}
```

On the JS side

```js
$(function() {
  Shiny.addCustomMessageHandler('bulma-notif', function(message) {
    if (message.id === undefined) {
      Bulma('body').notification(message.options).show();
    } else {
      Bulma('#' + message.id).notification(message.options).show();
    }
  });
});
```

Test app


```{r bulma-notif-test}
ui <- use_bulmajs(
  bulma_page(
    tags$head(
      tags$script(
        "$(function() {
          Shiny.addCustomMessageHandler('bulma-notif', function(message) {
            if (message.id === undefined) {
              Bulma('body')
                .notification(message.options)
                .show();
            } else {
              Bulma('#' + message.id)
                .notification(message.options)
                .show();
            }
          });
        });
        "
      )
    ),
    bulma_button("test", "Click me!", color = "warning")
  )
)

server <- function(input, output, session) {
  observeEvent(input$test, {
    show_bulma_notification(
      #id = "test", 
      options = list(
        body = "This is the message",
        color = "danger",
        dismissInterval = 2000
      )
    )
  })
}

shinyApp(ui, server)
```

### Modal
The other JS component is the modal. There are 2 steps, like in vanilla Shiny:

  - We first create the modal HTML
  - We ask JS to show/hide it
  
Alternatively, bulma JS allows to create the modal only from JS, like for notification. 
The latter approach avoids to insert the modal HTML in the UI (like in vanilla Shiny).
  
#### Modal HTML 
The bulma modal HTML is available in bulma's core [here](https://bulma.io/documentation/components/modal/) but only the card template works with bulma JS. After translating the most basic
HTML template to R, we create `bulma_modal`. Notice there are also other options, like the modal card.

```{r bulma-modal}
bulma_modal <- function(id, title = NULL, ...,
                        footer = tagList(
                          tags$button(
                            class = "button is-success",
                            "Save changes"
                          ),
                          tags$button(
                            class = "button is-danger is-outline",
                            "Cancel"
                          )
                        )
) {
  tags$div(
    id = id,
    class = "modal",
    tags$div(class = "modal-background"),
    tags$div(
      class = "modal-card",
      tags$header(
        class = "modal-card-head",
        tags$p(
          class = "modal-card-title",
          title
        ),
        tags$button(
          class = "delete",
          `aria-label` = "close"
        )
      ),
      tags$section(
        class = "modal-card-body",
        ...
      ),
      tags$footer(
        class = "modal-card-foot",
        footer
      )
    )
  )
}
```


#### Toggle the modal
Similar to `shiny::showModal` and `shiny::removeModal`, we could create `show_modal` and `hide_modal`. Let's do it with only 1 function, `toggle_bulma_modal`!

A shown modal has the `is-active` class. 

```js
$(function() {
  Shiny.addCustomMessageHandler('toggle-bulma-modal', function(message) {
    var modalId = '#' + message;
    var modal = Bulma(modalId).modal();
    if ($(modalId).hasClass('is-active')) {
      modal.close();
    } else {
      modal.open();
    }
  });
});
```


```{r toggle-bulma-modal}
toggle_bulma_modal <- function(id, session = shiny::getDefaultReactiveDomain()) {
  session$sendCustomMessage(type = "toggle-bulma-modal", id)
}
```


```{r bulma-modal-test}
ui <- use_bulmajs(
  bulma_page(
    tags$head(
      tags$script(
        "$(function() {
          Shiny.addCustomMessageHandler('toggle-bulma-modal', function(message) {
            var modalId = '#' + message;
            var modal = Bulma(modalId).modal();
            if ($(modalId).hasClass('is-active')) {
              modal.close();
            } else {
              modal.open();
            }
          });
        });
        "
      )
    ),
    bulma_modal("mymodal", "A modal", "This is my first modal!"),
    bulma_button("test", "Click me!", color = "warning")
  )
)

server <- function(input, output, session) {
  observeEvent(input$test, {
    toggle_bulma_modal(id = "mymodal")
  })
}

shinyApp(ui, server)
```

