---
title: "Custom Dropdown Menu Items"
author: "David Granjon"
date: "3/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(shiny)
library(shinydashboard)
```

## Intro
Have you ever wondered how to make shinydashboard `dropdownMenu` items (`messageItem`, `notificationItem`, `taskItem`) behaving like `actionButton` in Shiny?


### What is an action button?

Below is the code of the `actionButton`

```{r}
actionButton <- function (inputId, label, icon = NULL, width = NULL, ...)  {
  value <- restoreInput(id = inputId, default = NULL)
  tags$button(
    id = inputId, 
    style = if (!is.null(width)) paste0("width: ", validateCssUnit(width), ";"), 
    type = "button", 
    class = "btn btn-default action-button", 
    `data-val` = value, 
    list(validateIcon(icon), label), ...
  )
}
```

The button HTML tag has some attributes: id, style, type, class, `data-val`, label and children passed via `...`

### How does it work?
When the app starts, the action button has the value 0 and each click will increment its value by 1. 
How is this behaviour created? For each Shiny input element (radio, slider), there is an associated JavaScript magic file, called input binding, which you can find [here](https://github.com/rstudio/shiny/tree/master/srcjs). In our case, we are only interested in the action button binding:

```javascript
var actionButtonInputBinding = new InputBinding();
$.extend(actionButtonInputBinding, {
  find: function(scope) {
    return $(scope).find(".action-button");
  },
  getValue: function(el) {
    return $(el).data('val') || 0;
  },
  // ... other methods
});
```

What you see above is **not** the whole script since the goal is not to explain how an input binding works (It has already been done [before](https://shiny.rstudio.com/articles/building-inputs.html)). Instead, we will focus on the first method, that is `find`. The `find` method will look for **all** elements having the class **.action-button**, making it possible to define multiple action buttons at the same time.

Consequently, if we go back to the previous section, the `actionButton` contains **.action-button** in its class and will be considered by the binding (I aknowledge, this is not really interesting/surprising, at the moment). The input binding also needs the id attribute from the HTML tag. When bound, you can access it with input$... and perform actions on the server side.

### Apply it to other elements
What is interesting is that all elements having the class .action-button will be considered by the same shiny input binding. 

Disclaimer: some HTML tags will not be compatible with this approach


## Application

Let's apply this to the shinydashboard element we want to customize!

### Transform the `taskItem` function
Let's first have a look at the original function:

```{r}
taskItem <- function (text, value = 0, color = "aqua", href = NULL) 
{
    validateColor(color)
    if (is.null(href)) 
        href <- "#"
    tags$li(a(href = href, h3(text, tags$small(class = "pull-right", 
        paste0(value, "%"))), div(class = "progress xs", div(class = paste0("progress-bar progress-bar-", 
        color), style = paste0("width: ", value, "%"), role = "progressbar", 
        `aria-valuenow` = value, `aria-valuemin` = "0", `aria-valuemax` = "100", 
        span(class = "sr-only", paste0(value, "% complete"))))))
}
```

The most important part of this tag is that this item contains a link `a`, which we can seamlessly transform in an action button. If you remember, we **only** need 2 things:

- add the action-button class to the tag
- add an id attribute to access the input value later

Below is our new functions:

```{r}
taskItem2 <- function (inputId = NULL, text, value = 0, color = "aqua") {
  # validateColor(color) # this is not exported by shinydashboard
  tags$li(
    a(
      id = inputId,
      class = "action-button",
      href = "#",
      h3(text,
         tags$small(class = "pull-right", paste0(value, "%"))
      ),
      div(class = "progress xs",
          div(
            class = paste0("progress-bar progress-bar-", color),
            style = paste0("width: ", value, "%"),
            role = "progressbar",
            `aria-valuenow` = value,
            `aria-valuemin` = "0",
            `aria-valuemax` = "100",
            span(class = "sr-only", paste0(value, "% complete"))
          )
      )
    )
  )
}
```

**inputId** is a new parameter with NULL value by default. Besides, we removed the **href** parameter that conflicts with the new inputId. You could keep it but warn your users to choose either inputId or href.

### Add it to a shinydashboard example

```{r, eval=TRUE}
library(shiny)
shinyApp(
  ui = dashboardPage(
    dashboardHeader(
      dropdownMenu(
        type = "tasks", 
        badgeStatus = "danger",
        taskItem2(
          inputId = "mytask",
          value = 20, 
          color = "aqua",
          text = "Click me!"
        ),
        taskItem(
          value = 40, 
          color = "green",
          text = "Basic item"
        )
      )
    ),
    dashboardSidebar(),
    dashboardBody(),
    title = "Dashboard example"
  ),
  server = function(input, output) {
    observeEvent(input$mytask, {
     showModal(modalDialog(
        title = "Important message",
        "This is an important message!"
      ))
    })
  }
)
```

Now, each time you click on the first task item, a modal will show! Enjoy and stay safe ;)
