---
title: "shinybulma"
author: "David Granjon"
date: "9/27/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(htmltools)
```

## About bulma
[bulma](https://bulma.io/) is a more and more popular open source CSS framework for the web. Importantly, there **isn't** any JavaScript helper in the bulma core. We'll see later that the recent [bulma JS](https://bulmajs.tomerbe.co.uk/) provide such feature. For now, let's focus on HTML and CSS.

## Bulma: get started
The first thing to do is to review the **Getting started [guide](https://bulma.io/documentation/overview/start/)**. To install bulma dependencies, there are 3 way. For convenience, we'll choose the CDN method (content delivery network) which consists in getting dependencies from a dedicated server.
Obviously, an internet connection is required.

### Build the HTML dependency
```{r bulma-deps}
bulma_deps <- htmlDependency(
  name = "bulma",
  version = "0.9.0",
  src = c(href = "https://www.jsdelivr.com/package/npm/bulma"),
  stylesheet = "css/bulma.min.css"
)
```

```{r attach-bulma-deps}
use_bulma <- function(tag) {
  tagList(tag, bulma_deps)
}

# check it works ...
findDependencies(use_bulma(div()))
```
